---
title: "Visualization Part I"
output: github_document
---

```{r, echo=FALSE}
library(tidyverse)
library(ggridges)
```

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
## Registered S3 method overwritten by 'hoardr':
##   method           from
##   print.cache_info httr
## using cached file: ~/Library/Caches/R/noaa_ghcnd/USW00094728.dly
## date created (size, mb): 2022-04-04 04:13:35 (7.647)
## file min/max dates: 1869-01-01 / 2022-04-30
## using cached file: ~/Library/Caches/R/noaa_ghcnd/USC00519397.dly
## date created (size, mb): 2022-04-04 04:13:39 (1.697)
## file min/max dates: 1965-01-01 / 2020-02-29
## using cached file: ~/Library/Caches/R/noaa_ghcnd/USS0023B17S.dly
## date created (size, mb): 2022-04-04 04:13:42 (0.93)
## file min/max dates: 1999-09-01 / 2022-03-31

weather_df
## # A tibble: 1,095 × 6
##   name           id          date        prcp  tmax  tmin
##   <chr>          <chr>       <date>     <dbl> <dbl> <dbl>
## 1 CentralPark_NY USW00094728 2017-01-01     0   8.9   4.4
## 2 CentralPark_NY USW00094728 2017-01-02    53   5     2.8
## 3 CentralPark_NY USW00094728 2017-01-03   147   6.1   3.9
## 4 CentralPark_NY USW00094728 2017-01-04     0  11.1   1.1
## 5 CentralPark_NY USW00094728 2017-01-05     0   1.1  -2.7
## # … with 1,090 more rows
```
## Scatterplots!!

Create my first scatterplot ever

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point()
```

New approach, same plot

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

Save and edit a plot object. 

```{r}
weather_plot <- 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax))

weather_plot + geom_point()
```

## Advanced scatterplot 

Start with the same one and make it fancy! 

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```

What about the `aes` placement? 

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name)) + #up till here, no difference between the two
  geom_smooth(se = FALSE) #here - the placement of aes(color=name) makes a difference
```

Let's facet some things..

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = 0.2, size = 2) + 
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name) #this creates columns. facet_grid(name ~ .) creates rows
```

Let's combine some elements and try new plot

```{r}
weather_df %>%
  ggplot(aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha =.5) +
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```

## Small notes

How many geoms have to exist? 

You can have whatever geoms you want. 

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_smooth(se = FALSE)
```

You can use a neat geom! 

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_hex()
```

## Univariate plots

```{r}
weather_df %>%
  ggplot(aes(x = tmin)) +
  geom_histogram()
```

Can we add color..

```{r}
weather_df %>%
  ggplot(aes(x = tmin, fill = name)) + 
  geom_histogram(position = 'dodge')

weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) + 
  geom_histogram() + 
  facet_grid(. ~ name)
```
Let's try a new geometry

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) + 
  geom_density(alpha = 0.3, adjust = 0.5)
```

What about box plots? 

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin)) + 
  geom_boxplot()

```

Trendy blots 

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin, fill = name)) + 
  geom_violin(alpha = 0.5) + 
  stat_summary()
```

Ridge plots -- the most popular plot of 2017

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = name, fill = name)) + 
  geom_density_ridges()
```

## Save and Embed 

```{r}
weather_plot <- 
weather_df %>% 
  ggplot(aes(x = tmin, y= tmax, color = name)) + 
  geom_point(alpha = 0.5)

ggsave("./results/weather_plot.pdf", weather_plot, width = 8, height = 5)
```

What about embedding..

```{r}
weather_plot
```

Embed at different size 

```{r, fig.width = 12, fig.height = 6}
weather_plot
```
